Online learning apps from the learning cycle perspective: recent advances and best practices

### 2023-05-02 review_learning_dashboards_paper/paper.Rmd
Update paper.rmd

```{r, include=F}
#install.packages("igraph")
#install.packages("edgebundle")
#install.packages("edgebundleR")

library(igraph)
library(ggraph)
```

@@

#edges width
E(net2)$strength<-as.matrix(docss[docss>0])
E(net2)$width<-E(net2)$strength*0.25
edge.start2 <- ends(net2, es=E(net2), names=F)[,1]
edge.col2 <- V(net2)$color[edge.start2]
E(net2)$arrow.mode<-"-"

@@

>>>>

```{r, include=F}
#install.packages("igraph")
library(igraph)
```

@@

#edges width
E(net2)$strength<-c(t(docss)[t(docss)>0])
E(net2)$width<-E(net2)$strength*0.25
edge.start2 <- ends(net2, es=E(net2), names=F)[,1]
edge.col2 <- V(net2)$color[edge.start2]
E(net2)$arrow.mode<-"-"

@@

## Explore your own keywords and their relation to topics

As an example, we use an overarching topic "gamification" and keywords "game", "play", "excit".

```{r}
mykeywords<-c("game", "play", "excit")
#reduced dfm
mydfm_r<-mydfm[unique(as.numeric(as.matrix(tdocs))),]
ind0<-apply(mydfm_r,2,sum)!=0
mydfm_r<-mydfm_r[,ind0]

if (sum(mykeywords%in%colnames(mydfm_r))<length(mykeywords)){
  print(paste("omitting the missing keyword(s):",paste(mykeywords[!mykeywords%in%colnames(mydfm_r)],collapse=", ")))
  mykeywords<-mykeywords[mykeywords%in%colnames(mydfm_r)]
}

#per topic, compute the number of top 100 docs with these keywords/ or all docs but weighted by topic proportion
counts<-matrix(0,length(mykeywords)+K,length(mykeywords)+K)
for(i in 1:length(mykeywords)){
  for(j in 1:K){
    counts[i,j+length(mykeywords)]<-sum(mydfm[as.numeric(tdocs[,j]),mykeywords[i]])
  }
}
#counts per paper
pcounts<-matrix(0,nrow(tdocs),K)
for(i in 1:nrow(tdocs)){
  for(j in 1:K){
    pcounts[i,j]<-sum(mydfm[as.numeric(tdocs[i,j]),mykeywords])
  }
}

```{r}
#plot k networks: one keyword vs 9 topics
netk <- graph_from_adjacency_matrix((as.matrix(counts>0)))

#colors
kcols<-hcl.colors(max(length(mykeywords),2), palette = "green-orange", alpha = 0.8)

#vetrices size, color
V(netk)$size<-c(rep(0.1,length(mykeywords)),V(net)$topic_size)*300
V(netk)$color<-c(kcols[1:length(mykeywords)],rev(cols)[1:K])
V(netk)$label <- c(mykeywords,1:K)
V(netk)$shape <- c(rep("circle",length(mykeywords)),rep("circle",K))
V(netk)$label.color <- rep("black",K+length(mykeywords))

#edges width
E(netk)$width<-c(t(counts)[t(counts)>0]*0.25)
edge.start <- ends(netk, es=E(netk), names=F)[,1]
edge.col <- V(netk)$color[edge.start]
E(netk)$arrow.mode<-"-"
```

```{r}
#top papers
counts_total<-apply(counts,2,sum)[-(1:length(mykeywords))] # total counts of keywords per topic
tt<-order(counts_total, decreasing = T) #sort decreasing
howmany_topics<-5
tt<-tt[1:min(length(tt[counts_total>0]),howmany_topics)] #take at most howmany_topics with the keywords

howmany_papers<-3
ppapers<-NULL
for(i in 1:length(tt)){
  ppapers<-c(ppapers,works_search$display_name[tdocs[order(pcounts[,i], decreasing=T),tt[i]][1:howmany_papers]])
}

papers<-paste(rep(tt, each=howmany_papers), ppapers)
pcols<-c("gray66", "gray55", "gray44", hcl.colors(6, palette = "viridis", alpha = 1)[1:5],"indianred2")
pcols<-rep(rev(pcols)[tt],each=howmany_papers)
```

```{r}
par(mfrow=c(1,2),mar=c(0,0,1,0))
coords<-layout_in_circle(netk, order = V(netk))
plot(netk, layout=coords,edge.color=edge.col, edge.curved=0.1, main="Keyword relations")
legend("bottomleft", legend=paste(1:4,colnames(strength)[1:4]), border=F,pch=21,pt.bg=rev(cols)[1:4],bty="n",cex=0.6)
legend("bottomright", legend=paste(5:K,colnames(strength)[5:K]), border=F,pch=21,pt.bg=rev(cols)[5:K],bty="n",cex=0.6)

plot(c(0,1),c(0,1), axes=F, col=NA, main="Top papers", xlab="", ylab="")
par(xpd=T)
for(p in 1:length(papers)){
  text(0,1-(p-1)*length(papers)/220, papers[p], col=pcols[p],cex=0.7, pos=4)
}
